Manuscript for foodborne-outbreak Project

### 2023-02-24 products/manuscript/Manuscript.qmd
3
change in manuscript

---
title: "Example Manuscript Template for a Data Analysis Project"
subtitle: ""
author: Andreas Handel
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../references.bib
csl: ../apa.csl
editor: 
  markdown: 
    wrap: sentence
---

The structure below is one possible setup for a data analysis project (including the course project).
For a manuscript, adjust as needed.
You don't need to have exactly these sections, but the content covering those sections should be addressed.

This uses MS Word as output format.
[See here](https://quarto.org/docs/output-formats/ms-word.html) for more information.
You can switch to other formats, like html or pdf.
See [the Quarto documentation](https://quarto.org/) for other formats.

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(broom)
library(ggtext)
```

@@

*Provide enough background on your topic that others can understand the why and how of your analysis.*

@@

*Describe what the data is, what it contains, where it is from, etc. Eventually this might be part of a methods section.*

This dataset was uploaded onto Kaggle in 2017 and contains data from the Centers for Disease Control and Prevention (CDC) on foodborne disease outbreaks from 1998 to 2015 @centersfordiseasecontrolandprevention2017.
There are 12 variables and 16,950+ observations.
The raw data may be viewed within the repository of this project.

@@

We expect to see that outbreaks occur most often in homes rather than restaurants, the pathogen most commonly seen to be *E. coli*, and for the food most often associated with outbreaks to be some form of salad.

@@

To cite other work (important everywhere, but likely happens first in introduction), make sure your references are in the bibtex file specified in the YAML header above (here `dataanalysis_template_references.bib`) and have the right bibtex key.
Then you can include like this:

Examples of reproducible research projects can for instance be found in [@mckay2020; @mckay2020a]

@@

1.  Data wrangling: handling the missing values and cleaning inconsistent data.
2.  Selecting the interested predictors and outcomes to plot their relationships.
3.  If the graphs indicate any significant or interesting trend, we will conduct a general linear model and omnibus test.
4.  Post-hoc test to identify the significant difference between levels.
5.  Mapping cases with different predictors across the states.

@@

As previously mentioned, the data was acquired from [Kaggle](https://www.kaggle.com/datasets/cdc/foodborne-diseases).

@@

*Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along.*

>>>>

---
title: "Manuscript for foodborne-outbreak Project"
subtitle: ""
author: Andreas Handel
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../references.bib
csl: ../apa.csl
editor: 
  markdown: 
    wrap: sentence
---

set up
```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(broom)
library(ggtext)
```

@@

@@

We adopted two datasets for this study. The first dataset was uploaded onto Kaggle in 2017 and contains data from the Centers for Disease Control and Prevention (CDC) on foodborne disease outbreaks from 1998 to 2015 @centersfordiseasecontrolandprevention2017.
There are 12 variables and 16,950+ observations.
The second dataset was collected from National Outbreak Reporting System (NORS), Centers for Disease Control and Prevention (CDC) website. This dataset covers the reports of foodborne and waterborne disease outbreaks and enteric (intestinal) disease outbreaks spread by contact with environmental sources, infected people or animals, and other means from 2009 to 2020.
The raw datasets may be viewed within the repository of this project.

@@

We expect to see that outbreaks occur most often in homes rather than restaurants, the pathogen most commonly seen to be *E. coli*, and for the food most often associated with outbreaks to be some form of salad.
Moreover, we want to predict the accuracy of the model trained by first dataset using the second dataset as testing data.

@@

To cite other work (important everywhere, but likely happens first in introduction), make sure your references are in the bibtex file specified in the YAML header above (here `dataanalysis_template_references.bib`) and have the right bibtex key.

@@

1.  Data wrangling: handling the missing values and cleaning inconsistent data.
2.  Selecting the interested predictors and outcomes to plot their relationships.
3.  If the graphs indicate any significant or interesting trend, we will conduct a general linear model and omnibus test.
4.  Post-hoc test to identify the significant difference between levels.
5.  Mapping cases with different predictors across the states.
6.  Applying Machine learning approach to test the model accuracy.

@@

As previously mentioned, the data was acquired from [Kaggle](https://www.kaggle.com/datasets/cdc/foodborne-diseases) and [CDC] (https://wwwn.cdc.gov/norsdashboard/).

@@

*Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along.*
```{r}
#The detailed cleaning process can be found in the file located in ("code","processing","
```
